\normalfont\spacedallcaps{Suggested Project Goal B}

### 2017-06-03 latex/article.tex
Added table with LDA topics' relevant terms

			%TODO: Inserire tabella con un po' di topic significativi

>>>>

			Nella tabella \ref{table:ldatopics} sono elencati i 10 termini più rilevanti per alcuni dei topic risultati dall'applicazione di LDA con $k=80$.

			\begin{table}[!htbp]
			\vspace*{0.2cm}
			\hspace*{1cm}
			\begin{tabular}{l|l}
			Topic 1 & plant tree food forest bird fish animal flower grow natural\\
			Topic 2 & film series episode star character movie actor direct role television\\
			Topic 3 & building house build tower hall hotel wall room floor design\\
			Topic 4 & church catholic bishop saint st. roman bell pope cathedral rome\\
			Topic 5 & league season sign play manager baseball contract appearance professional pitch\\
			\end{tabular}
			\caption{Alcuni topic individuati da LDA con i termini associati pi\`{u} rilevanti}
			\label{table:ldatopics}
			\end{table}
